%chapter 3, Tom Mulvey, 2/27/18
\documentclass[12pt]{article}

%do i even need to include these lol
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{xcolor}

%new macros for r,q,n,z
\newcommand{\Q}{\mathbb Q}
\newcommand{\N}{\mathbb N}
\newcommand{\Z}{\mathbb Z}
\newcommand{\R}{\mathbb R}
\newcommand{\ind}{\hspace{10mm}}

\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{rem}[thm]{Remark}
\newtheorem{conj}[thm]{Conjecture}

\begin{document}

\centerline{\sc \large Homework 3 | Tom Mulvey }

\centerline{\sc 2/27/18}

\vspace{2pc}

\begin{enumerate}

\item[3.8] ) Prove if x is an odd int, then 9x+5 is even
   \begin{proof}  
      Assume $x$ is an odd integer, then..

      $x=2k+1$ for some $k \in \Z$
      
      It follows that $9x+5$=$9(2k+1)+5$

      =$18k+14$

      =$2(9k+7)$ where 9k+7 is an integer

      This is obvioulsy even.
   \end{proof}
\item[3.20] )
   \begin{proof} $let x\in \Z$ Prove that $3x+1$ is even $\iff$ $5x-2$ is odd
	
      \begin{lem}
         Let $x \in \Z$. If $3x+1$ is even then $x$ is odd.


	 Proof (lemma):We will prove this lemma by the contrapositive appproach. If $x$ is even, then $3x+1$ is odd. If $x$ is even, it follows that $x$ = $2k$ for some $k \in \Z$ 


         $3x+1$ $=3(2k) +1$ $=3*$an even integer$ +1$

	 This is obviously odd.
      \end{lem}	
      Proof: Fot the forward direction, I will prove directly. $Let 3x+1$ be an even integer. by the lemma,the integer $x$ is od. Since $x$ is odd, $x=2k+1$ for some $k \in \Z$. Thus

      $5x-2=5(2k+1)-2=10k+5-2=10k+3$
      
      $=3(2k+1) + 4k$

      $=3(2k+1) + 2(2k)$

      $=3*$an odd integer + an even integer

      $=$an odd integer

       For the reverse direction, I will prove by the contrapositive. 

       The proof is similar in the reverse direction as the forward.
   \end{proof}
\item[3.26] ) Prove that if $n \in \Z$ then $n^2 -3n +9$ is odd.
   \begin{proof}
      I will argue by cases that if $n$ is either odd OR even, $n^2 -3n +9$ is odd.


      CASE 1: $n$ is even
      $\ind$If $n$ is even, it follows that $n$=$2k$ for some $k \in \Z$

      $\ind$thus $n^2-3n+9$ = $(2k)^2 -3(2k) + 9$
 
      $\ind$=$4k^2-6k+9$

      $\ind$=$4k^2-3(2k+3)$

      $\ind$=even integer - 3*(odd integer)

      $\ind$odd integer

      CASE 2: $n$ is odd
      
      $\ind$If $n$ is odd, it follows that $n=2k+1$ for some $k \in \Z$

      $\ind$thus $n^2-3n+9$ = $(2k+1)^2 -3(2k+1) + 9$a

      $\ind$=$4k^2+4k+1-6k-3+9$

      $\ind$=$4k^2-2k+7$

      $\ind$=$2(2k^2-1k)+7$

      $\ind$=even integer + odd integer
   
      $\ind$=obviously odd

   $n^2-3n+9$ is odd when $n$ is odd or evena
   \end{proof}

\end{enumerate}
\end {document}
